Modeling browser-based distributed evolutionary computation systems

### 2015-02-06 modeling-volunteer-computing-gecco.tex
Having a shot at it

\documentclass[a4paper]{article}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx,epsfig}
\usepackage{listings}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[affil-it]{authblk}

%%%%

\usepackage{color}
\usepackage{alltt}
\usepackage{verbatim}
\usepackage{url}

@@

\title{Modeling browser-based evolutionary computation systems}
%\author{Juan J. Merelo-Guervós}
\author{Som E. One}
\affil{Somewhere Institute}

@@

\section{What is the point of low or no cost evolutionary algorithms?}

@@

In this talk we will offer our experience on using browser-based computing since 1999 \cite{jesusIWANN99} and other emerging paradigms, such as peer to peer based computing \cite{evag:gpem}, mainly applied to the design of evolutionary algorithms.

@@

\bibliographystyle{splncs}
\bibliography{geneura,volunteer}

>>>>

\documentclass{sig-alternate}

\usepackage[latin1]{inputenc}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\title{Modeling browser-based distributed evolutionary computation systems}

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Som E. One\\
       \affaddr{Some Institute}\\
       \email{em@a.il}
}

@@

\keywords{Evolutionary computation, volunteer computing, distributed
  computing, node.js, javascript}

\section{Introduction}

@@

In this paper we will offer our experience on using browser-based computing since 1999 \cite{jesusIWANN99} and other emerging paradigms, such as peer to peer based computing \cite{evag:gpem}, mainly applied to the design of evolutionary algorithms.

@@

\bibliographystyle{abbrv}
\bibliography{geneura,volunteer}
